Report on Late Winter2013 Production: Image Differencing

### 2013-03-28 W13report.tex

\subsection{Detection Threshold {\bf SIMON}}

Section \ref{sec-analyticfp} discusses the theoretical foundation 
that sets the floor on the number of false positives we expect from a 
pure Gaussian random field.  The number of false positives is a strong
function of the seeing and and the confidence level of the detection.  
By comparing the empirical false positive rate to the analytic predictions
we can quantify how close we are getting to the theoretical floor in these
data.  Because the number of false positives is such a strong function of
detection threshold, misestimation of the signal to noise of the detections
has a large impact on how many false positives are observed.

The Figure \ref{fig-fpthresh} shows the 
effect of misestimating the noise in the detections for each of three different
seeing values (0.6\", 0.88\", 1.2\" respectively).  In each case the top panel shows
the number additional false positives in an LSST size CCD given a fractional misestimation
of the noise in the image and a detection threshold.  A 1\% under-estimate of the noise
corresponds to ~4 additional false positives at a threshold of $5\sigma$ in the best seeing case.  
The bottom panel shows 
the effect of over-estimating the noise in the measurement.  The effect is to reduce
the number of false positives.  A 1\% under-estimate of the noise results in 2 fewer false positives
per chip.

@@

\begin{figure}
\includegraphics[width=0.8\textwidth]{figures/fp_v_dsky.eps}
\caption{
Misestimation of the sky value has an effect on both the number of false positives and relative abundance of positive false positives to negative false positives.
The top pane of this figure shows the relative number of +ve/-ve (-ve/+ve) if the sky background is under (over) subtracted at a particular fractional level.  The 
bottom panel shows how the total number of false positives changes for the same misestimation.  This is not a strong function of the seeing, so only the best
seeing example is shown.
}
\label{fig-skythresh}
\end{figure}

>>>>

\subsection{Effect of Uncertainty on Measured ${S}\over{N}$ {\bf SIMON}}

Section \ref{sec-analyticfp} discusses the theoretical foundation 
that sets the floor on the number of false positives we expect from a 
pure Gaussian random field.  The number of false positives is a strong
function of the seeing and the confidence level of the detection.  
By comparing the empirical false positive rate to the analytic predictions
we can quantify how close we are getting to the theoretical floor in these
data.  Because the number of false positives is such a strong function of
detection threshold, misestimation of the signal to noise of the detections
has a large impact on how many false positives are observed.

The Figure \ref{fig-fpthresh} shows the 
effect of misestimating the noise in the detections for each of three different
seeing values (0.6$^{\prime\prime}$, 0.88$^{\prime\prime}$, 1.2$^{\prime\prime}$ respectively).  In each case the top panel shows
the number additional false positives in an LSST size CCD given a fractional misestimation
of the noise in the image and a detection threshold.  A 1\% under-estimate of the noise
corresponds to ~4 additional false positives at a threshold of $5\sigma$ in the best seeing case.  
The bottom panel shows 
the effect of over-estimating the noise in the measurement.  The effect is to reduce
the number of false positives.  A 1\% under-estimate of the noise results in 2 fewer false positives
per chip.

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/fp_v_dsky.eps}
\caption{
Misestimation of the sky value has an effect on both the number of false positives and relative abundance of positive false positives to negative false positives.
The top pane of this figure shows the relative number of +ve/-ve (-ve/+ve) if the sky background is under (over) subtracted at a particular fractional level.  The 
bottom panel shows how the total number of false positives changes for the same misestimation.  This is not a strong function of the seeing, so only the best
seeing example is shown.
}
\label{fig-skythresh}
\end{figure}
